\documentclass[12pt,openany]{StyleBertrand}
\author{Bertrand Guerrero}
\usepackage{etex}
\usepackage{lmodern}
\renewcommand{\familydefault}{\rmdefault}
\usepackage[francais]{babel}
\usepackage[T1]{fontenc}
\usepackage[utf8x]{inputenc}
\usepackage[a4paper]{geometry}
\geometry{verbose,tmargin=3.5cm,bmargin=3cm,lmargin=3cm,rmargin=2cm,headsep=1.75cm}
%\setcounter{secnumdepth}{4}
%\setcounter{tocdepth}{4}
\addto\extrasfrench{%
   \providecommand{\og}{\leavevmode\flqq~}%
   \providecommand{\fg}{\ifdim\lastskip>\z@\unskip\fi~\frqq}%
}
\usepackage[thinlines]{easymat}
\usepackage{lscape}
\usepackage{pslatex}
\usepackage{txfonts}
\usepackage{footnote}
%\usepackage{mathptmx}
\usepackage{setspace}
%\usepackage{natbib}
\onehalfspacing
\usepackage[unicode=true,
 bookmarks=true,bookmarksnumbered=false,bookmarksopen=false,
 breaklinks=true,pdfborder={0 0 0},backref=false,colorlinks=true, citecolor=Gray, linkcolor=blue, urlcolor=blue]
 {hyperref}
%\usepackage{numprint}
\usepackage{breakurl}
\usepackage{graphics}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{here}
\usepackage{float}
\usepackage[french, ruled, vlined]{algorithm2e}
\graphicspath{{Images/}}
\usepackage{caption}
\usepackage{subcaption}
\captionsetup{figurewithin=none}  
\captionsetup{tablewithin=none}
\usepackage{lettrine}
\renewcommand{\LettrineFontHook}{\color[gray]{0.5}}
\usepackage[svgnames]{xcolor}
\xdefinecolor{DarkOliveGreen}{named}{DarkOliveGreen}
\usepackage{multirow}
\usepackage{float}
%\everymath{\color{DarkOliveGreen}}
\usepackage{wrapfig}
\usepackage[]{tocbibind}
\usepackage{makeidx}
\usepackage{textcomp}
\usepackage[final]{pdfpages} 





\makeatletter



\makeindex
\newenvironment{changemargin}[2]{\begin{list}{}{%
\setlength{\topsep}{0pt}%
\setlength{\leftmargin}{0pt}%
\setlength{\rightmargin}{0pt}%
\setlength{\listparindent}{\parindent}%
\setlength{\itemindent}{\parindent}%
\setlength{\parsep}{0pt plus 1pt}%
\addtolength{\leftmargin}{#1}%
\addtolength{\rightmargin}{#2}%
}\item }{\end{list}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.
%% Because html converters don't know tabularnewline
\providecommand{\tabularnewline}{\\}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Textclass specific LaTeX commands.
\usepackage{enumitem}		% customizable list environments
\newlength{\lyxlabelwidth}      % auxiliary length 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
\renewcommand{\thefigure}{\ifnum \c@chapter>\z@ \thechapter.\fi
 \@arabic\c@figure}
\@addtoreset{figure}{chapter}

\renewcommand{\thetable}{\ifnum \c@chapter>\z@ \thechapter.\fi
 \@arabic\c@table}
\@addtoreset{table}{chapter}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Insertion de code Java
\usepackage{listings}
\lstset{
language=Java,
basicstyle=\normalsize, % ou ça==> basicstyle=\scriptsize,
upquote=true,
aboveskip={1.5\baselineskip},
columns=fullflexible,
showstringspaces=false,
extendedchars=true,
breaklines=true,
showtabs=false,
showspaces=false,
showstringspaces=false,
identifierstyle=\ttfamily,
keywordstyle=\color[rgb]{0,0,1},
commentstyle=\color[rgb]{0.133,0.545,0.133},
stringstyle=\color[rgb]{0.627,0.126,0.941},
}

\begin{document}

\chapter*{Abstract}

Within MobiGIS\footnote{\url{http://www.mobigis.fr/}}, publisher of GIS and Transport software and geomatics service company, I joined the Research \& Development \og MobiSAAS \fg project. \\

My internship subject focuses on developing web services that expose functionalities of road and transit data import, for automatic build of multi-modal transport networks. \\

The objective of my work is to expose functionalities originally coded in SQL and/or Python language via a REST API in Java (JAX-RS). So I initially took over the business treatment (Python) and learned to manipulate data (PostGIS/SQL) via the \og DataWizard \fg project. In the same time, in order to implement these web services I joined the \og MobiSAAS \fg project and so learned to develop with the \og Dropwizard \fg framework. \\

The developed application of this project presents like a SAAS\footnote{\url{https://en.wikipedia.org/wiki/Software_as_a_service}} the main features of MobiAnalyst Desktop software. It is in the context of the administration interface (backend) I develop features to upload transit data (GTFS\footnote{\url{https://developers.google.com/transit/gtfs/}}). The prospects of my work will be to generalize the utility classes and methods I have developed so that the application could support multiple data formats of other transport data format (vector data \og Shapefile \fg for example). \\

During this internship I worked on several projects: MobiSAAS, DataWizard, Crislab, etc. So I participated in various phases of software development lifecycle : from the design R\&D (MobiSAAS) to development of business code (DataWizard), until delivery to the customer (Crislab). \\

\end{document}